---
title: "Visualization of Stochastic Processes"
output: html_document
author: Wenyao Sha
date: "`r format(Sys.time(), '%Y-%m-%d')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rgl)
library(htmlwidgets)
library(purrr)

setwd("C:/Users/Wenyao/Desktop/R/Visualization-of-Stochastic-Processes")
source("./functions.R")

plot_size <- 400
plot_step <- 50
```

<br><br>

Stochastic process makes for an excellent source of visualization. In this demo, I show the dynamics of stochastic processes along the three physical diemensions:

* $t$: time
* $x$: the value of the stochastic process at time $t$
* $f(x)$: the probability density (or the probablity mass in the discrete case) of $x$ at time $t$

Note that the expected value (or the closest permissible value in the discrete case) at each time $t$ is also highlighted.

All plots are meant to be interactive. Drag to rotate and scroll to zoom in/out on WebGL-compatable devices. Certain feature like drift, dispersion, mean-reversion or non-negativeness might be more clearly visible from a different angle.

<br><br>

### Trend Stationary Model (without Drift)
$X_t = X_0 + \epsilon_t$
```{r echo = FALSE, warning = FALSE}
# Trend Stationary without slope
tn1 <- plot_trend_stationary(beta = 0, sigma = 1, x0 = 0, xlim = c(0, 5), ylim = c(-5, 5), step = plot_step)

rglwidget(
  width = plot_size,
  height = plot_size
) 
```

<br><br><br><br>

### Trend Stationary Model
$X_t = X_0 + \beta t + \epsilon_t$
```{r echo = FALSE, warning = FALSE}
# Trend Stationary with slope
tn2 <- plot_trend_stationary(beta = 1, sigma = 1, x0 = 0, xlim = c(0, 5), ylim = c(-5, 5), step = plot_step)

rglwidget(
  width = plot_size,
  height = plot_size
) 
```

<br><br><br><br>
  
### Brownian Motion (without Drift)
$dX_t = \sigma dW_t$
```{r echo = FALSE, warning = FALSE}
bm1 <- plot_brownian_motion(miu = 0, sigma = 1, x0 = 0, xlim = c(0, 5), ylim = c(-5, 5), step = plot_step)

rglwidget(
  width = plot_size,
  height = plot_size
) 
```

<br><br><br><br>

### Brownian Motion
$dX_t = \mu t + \sigma dW_t$
```{r echo = FALSE, warning = FALSE}
bm2 <- plot_brownian_motion(miu = 1, sigma = 1, x0 = 0, xlim = c(0, 5), ylim = c(-5, 5), step = plot_step)

rglwidget(
  width = plot_size,
  height = plot_size
) 
```

<br><br><br><br>

### Brownian Bridge
$X_t = \frac{t}{T} X_T + \frac{T-t}{T} (X_0 + \sigma W_t)$
```{r echo = FALSE, warning = FALSE}
bb <- plot_brownian_bridge(sigma = 1, initial_value = 5, terminal_value = 0, term = 5, xlim = c(0, 5), ylim = c(0, 6), step = plot_step)

rglwidget(
  width = plot_size,
  height = plot_size
) 
```

<br><br><br><br>

### Geometric Brownian Motion
$dX_t = \mu X_t t + \sigma X_t dW_t$
```{r echo = FALSE, warning = FALSE}
gb <- plot_geo_brownian_motion(miu = 0.1, sigma = 0.5, x0 = 2.5, xlim = c(0, 5), ylim = c(-1, 5), step = plot_step)

rglwidget(
  width = plot_size,
  height = plot_size
) 
```

<br><br><br><br>

### Vasicek Model
$dX_t = a(b-X_t)dt + \sigma dW_t$
```{r echo = FALSE, warning = FALSE}
vasicek <- plot_vasicek(a = 1, b = 3, sigma = 1, x0 = 0.01, xlim = c(0, 5), ylim = c(-1, 4), step = plot_step)

rglwidget(
  width = plot_size,
  height = plot_size
) 
```

<br><br><br><br>

### Cox–Ingersoll–Ross Model
$dX_t = a(b-X_t)dt + \sigma \sqrt{X_t}dW_t$
```{r echo = FALSE, warning = FALSE}
CIR <- plot_CIR(a = 1, b = 3, sigma = 2, x0 = 0.01, xlim = c(0, 5), ylim = c(-1, 4), step = plot_step)

rglwidget(
  width = plot_size,
  height = plot_size
) 
```

<br><br><br><br>

### Poisson Process
$P(X_t = k) = e^{-\lambda t} \frac{(\lambda t) ^ k}{k\,!}$
```{r echo = FALSE, warning = FALSE}
poisson <- plot_poisson(lambda = 10, x0 = 0, xlim = c(0, 5), ylim = c(-5, 50), step = plot_step)

rglwidget(
  width = plot_size,
  height = plot_size
)
```

<br><br><br><br>

### Compensated Poisson Process
$X_t = N_t - \lambda t$
```{r echo = FALSE, warning = FALSE}
comp_poisson <- plot_comp_poisson(lambda = 10, x0 = 0, xlim = c(0, 5), ylim = c(-25, 25), step = plot_step)

rglwidget(
  width = plot_size,
  height = plot_size
)
```

<br><br><br><br>

```{r echo = FALSE, warning = FALSE}
rgl.clear()
```
