---
title: "Visualization of Stochastic Processes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(rgl)
library(htmlwidgets)
library(purrr)

setwd("C:/Users/Wenyao/Desktop/R/Visualization-of-Stochastic-Processes")
source("./functions.R")

plot_size <- 400
```

<br>

Drag to rotate and scroll to zoom in/out on WebGL-compatable devices.  

### Trend Stationary Model (without Drift)
$X_t = X_0 + \epsilon_t$
```{r echo = FALSE, warning = FALSE}
# Trend Stationary without slope
tn1 <- plot_trend_stationary(beta = 0, sigma = 1, x0 = 0, xlim = c(0, 5), ylim = c(-5, 5), step = 50)

rglwidget(
  width = plot_size,
  height = plot_size,
) 
```

<br><br><br><br>

### Trend Stationary Model
$X_t = X_0 + \beta t + \epsilon_t$
```{r echo = FALSE, warning = FALSE}
# Trend Stationary with slope
tn2 <- plot_trend_stationary(beta = 1, sigma = 1, x0 = 0, xlim = c(0, 5), ylim = c(-5, 5), step = 50)

rglwidget(
  width = plot_size,
  height = plot_size,
) 
```

<br><br><br><br>
  
### Brownian Motion (without Drift)
$dX_t = \sigma dW_t$
```{r echo = FALSE, warning = FALSE}
bm1 <- plot_brownian_motion(miu = 0, sigma = 1, x0 = 0, xlim = c(0, 5), ylim = c(-5, 5), step = 50)

rglwidget(
  width = plot_size,
  height = plot_size,
) 
```

<br><br><br><br>

### Brownian Motion
$dX_t = \mu t + \sigma dW_t$
```{r echo = FALSE, warning = FALSE}
bm2 <- plot_brownian_motion(miu = 1, sigma = 1, x0 = 0, xlim = c(0, 5), ylim = c(-5, 5), step = 50)

rglwidget(
  width = plot_size,
  height = plot_size,
) 
```

<br><br><br><br>

### Geometric Brwonian Motion
$dX_t = \mu X_t t + \sigma X_t dW_t$
```{r echo = FALSE, warning = FALSE}
gb <- plot_geo_brownian_motion(miu = 0.1, sigma = 0.5, x0 = 2.5, xlim = c(0, 5), ylim = c(-1, 5), step = 50)

rglwidget(
  width = plot_size,
  height = plot_size,
) 
```

<br><br><br><br>

### Vasicek Model
$dX_t = a(b-X_t)dt + \sigma dW_t$
```{r echo = FALSE, warning = FALSE}
vasicek <- plot_vasicek(a = 1, b = 3, sigma = 1, x0 = 0.01, xlim = c(0, 5), ylim = c(-1, 4), step = 50)

rglwidget(
  width = plot_size,
  height = plot_size,
) 
```

<br><br><br><br>

### Cox–Ingersoll–Ross Model
$dX_t = a(b-X_t)dt + \sigma \sqrt{X_t}dW_t$
```{r echo = FALSE, warning = FALSE}
CIR <- plot_CIR(a = 1, b = 3, sigma = 2, x0 = 0.01, xlim = c(0, 5), ylim = c(-1, 4), step = 50)

rglwidget(
  width = plot_size,
  height = plot_size,
) 

rgl.clear()
```

<br><br><br><br>
